Summary Tables

### 2019-04-09 summary_tables.Rmd
Use a global var to round to a specific value

@@

scen_prop <- round(io$scen_prop, 2)

@@

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  df1 <- df %>% filter(scenario == "Baseline") %>% group_by(trip_id, trip_mode, scenario)
  u_trips <- nrow(df1)
  td <- df %>% group_by(trip_id, trip_mode, scenario) %>% group_by(trip_mode, scenario) %>% summarise(p = round(n() /  u_trips * 100, 2)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td[2:6, 1] <- rownames(scen_prop)
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

@@

for(city in cities){
    td <- io[[city]]$dist %>% mutate_if(is.numeric, round, digits = 2)
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Distance table for ", city)))
    cat("\n")
}

@@

for(city in cities){
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = 2)
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table for ", city)))
    cat("\n")
}

>>>>

# round to
round_to <- 1

@@

scen_prop <- round(io$scen_prop, round_to)

@@

for(city in cities){
  df <- io[[city]]$trip_scen_sets
  df1 <- df %>% filter(scenario == "Baseline") %>% group_by(trip_id, trip_mode, scenario)
  u_trips <- nrow(df1)
  td <- df %>% group_by(trip_id, trip_mode, scenario) %>% group_by(trip_mode, scenario) %>% summarise(p = round(dplyr::n() /  u_trips * 100, round_to)) %>% spread(key = trip_mode, value = p) %>% mutate(row_sums = rowSums(.[sapply(., is.numeric)], na.rm = TRUE))
  td[2:6, 1] <- rownames(scen_prop)
  print(kable(td, caption = paste("Trip proportion (%) by mode for ", city)))
  cat("\n")
}

@@

for(city in cities){
    td <- io[[city]]$dist %>% mutate_if(is.numeric, round, digits = round_to)
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Distance table for ", city)))
    cat("\n")
}

@@

for(city in cities){
    td <- io[[city]]$dur %>% mutate_if(is.numeric, round, digits = round_to)
    colnames(td)[3:7] <- rownames(scen_prop)
    print(kable(td, caption = paste("Duration table for ", city)))
    cat("\n")
}
